\huge\bf{Querypoint} : Moving Backwards on Wrong Values in the Buggy Execution

### 2011-06-08 papers/fse-tool2011/sig-alternate.tex

% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%
\end{document}

>>>>

% You must have a proper ".bib" file
%  and remember to run:
% latex bibtex latex latex
% to resolve all references
%
% ACM needs 'a single self-contained file'!
%

\appendix
\section{Presentation}
The presentation will include the follwing parts:
\begin{enumerate}
	\item A short demo, debugging a simple buggy web page by the tool.
	\item A brief explanation of \textit{lastChange} algorithm.
	\item A brief explanation on \textit{Querypoint} debugging as a general debugging approach.
	\item Discussion about non-deterministic reproducible executions.
	\item A comprehensive demo on the Tool features.
\end{enumerate}

\section{Tool Maturity}
The tool is functional, however this is the first version of \textit{Querypoint} and therefore it is 
not mature enough to be used by developers working in industry.

\section{Resources}
The tool and its source code are publicly available and can be downloaded 
from \textit{Querypoint Debugging} web site at this address:

\mbox{\href{http://code.google.com/p/querypoint-debugging}{http://code.google.com/p/querypoint-debugging}}

The details of our user study, including the instructions and test cases source code, are available at this address:

\mbox{\href{http://ltiwww.epfl.ch/~mirghase/lastchange-userstudy}{http://ltiwww.epfl.ch/\texttildelow mirghase/lastchange-userstudy}}

\end{document}
